Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators

### 2019-08-30 GWLDCII.tex
Through section 4

\begin{lem}\label{lem sian}
  Let $W$ be a weakly admissible WLD with at least 5 vertices and in which each vertex supports at least one propagator.  Then at least one of the following two things occurs.
  \begin{enumerate}
    \item $W$ has a propagator of length $\leq 6$ with a propagator of length 2 on one side of it and nothing else on that side.\label{item big and 2}
    \item There exists a pair of propagators of length $2$ with the property that the first propagator is $(i, i+2)$, the second is $(j, j+2)$, no other propagator ends between vertices $i+2$ and $j+1$, and $j\in\{i+2, i+3, i+4\}$.\label{item pair of 2s}
  \end{enumerate}
\end{lem}
\note{Should this lemma have pictures}

@@

\begin{rmk} \label{clockwise ordering rem}
When $p$ contributes $I_i(p) = a$, it must be the clockwise-most propagator amongst those not yet assigned that is supported on $a$ i.e. any propagator assigned later that is supported on $a$ must be inside $(p, <_{a-1})$.
\end{rmk}

@@

 \note{Remember to keep an eye out when proofreading: do we just need the vertices appearing in the GN element to be the same, or do we actually need the functions to match up}

@@

Let $W = (\cP,[n])$ be an admissible Wilson loop diagram\st{, and}{\color{violet}. For every }$p = (i,j) \in \cP$\st{.  Then}{\color{violet}, the sets} $J_p^{W}(i)$, $J_p^{W}(i+1)$, $J_p^{W}(j)$, and $J_p^{W}(j+1)$ are each non-empty cyclic intervals which partition $[n]$ and occur in the given cyclic order.
\end{lem}

\begin{proof}
We will prove the result by induction on the number of propagators.  If $W$ has one propagator then the result is immediate.  Now suppose $W$ has more than one propagator.  Since non-supporting vertices have no effect on Algorithm~\ref{alg:put GN on WLD}, it suffices to prove the result for $W$  (possibly weakly admissible) with \st{$F(\emptyset) = \emptyset$}{\color{violet} no non-supporting vertices}.  Then by Lemma~\ref{lem sian}, $W$ has at least one of the four situations illustrated in Figure~\ref{fig 3 cases}.

@@

We first calculate $I^{W}_w$ for a starting vertex ${w \in [n]\backslash \{l, l+1, \ldots,j,j+1\}}$. \hlfix{Note that $p$ has no effect on other propagators for starting vertices in this range,}{By rmk \ref{rmk algorithm locally same}? If so, the entire proof depends on this fact. We should state it prominently and move on.} so if $r \neq p$, then $I_w^W(r) = I_w^V(r)$. Meanwhile, the value of $I^{W}_w(p)$ depends on which step in the algorithm the propagator $q$ \hlfix{is assigned to}{was this the one place where we has agreed to keep assigned instead of contributes?} a vertex {\color{violet} in the diagram $V$}, i.e. on the value of $I^{V}_w(q)$. Thus, if $w\in J_q^{V}(i)$ then 
    \[
    I_w^{W}(r) =  \begin{cases}
        \max\{i+1, m\} & \text{if } r=p \\
        I_{w}^{V}(r) & \text{if } r\neq p
      \end{cases} 
    \]
    while if $w\in J_q^{V}(i+1)$ or $w\in J_q^{V}(j)$ then
    \[
    I_w^{W}(r) =  \begin{cases}
        l & \text{if } r=p \\
        I_{w}^{V}(r) & \text{if } r\neq p
      \end{cases} 
      \]
We also need to understand $I^{W}_w$ for $w \in \{l,l+1,\ldots,j,j+1\}$. For the majority 
%$w \in [l, l+a-1]$} 
%I left this as a comment so we can add it in if necessary, but I don't think we need this level of precision in this sentence: we're just signposting what we're going to do in detail shortly.
of these vertices, we use the following observation: if $p$ is the first propagator to be assigned a value by $I_w^{W}$, then the remainder of $I_w^{W}$ proceeds identically to the assignments of $I^{V}_{w+1}$ (recall Remark~\ref{rmk algorithm locally same}).  Thus we have for any $0\leq b <a$
    \[
    I_{l+b}^{W}(r) = \begin{cases}
      l+b & \text{if } r=p\\
      I_{l+b+1}^{V}(r) & \text{if } r\neq p
    \end{cases}
    \]
Similarly, if $j$ is in the support of $p$, then we have
     \[
       I_j^{W}(r) = \begin{cases}
         j & \text{if $r=p$ and $j$ is in the support of $p$}\\
         I_{j+1}^{V}(r) & \text{if $r\neq p$ and $j$ is in the support of $p$}\\
       \end{cases}
       \]
If $j$ is not in the support of $p$, then we must be in Case 2 of Figure~\ref{fig 3 cases} with two vertices in the right hand region.  In this case, if we start the algorithm at $j$ we need to know whether there will be any unassigned propagators other than $p$ when we reach vertex $i$, so as to know what $p$ contributes.

@@

\begin{lem}\label{lem good p}
  Let $W$ be an admissible Wilson loop diagram with \hlfix{$n\geq 1$}{$k \geq 1$? $n$ is the number of vertices?} propagators.  Then there is some dihedral transformation of $W$ such that the resulting diagram $W'$ has a propagator $p$ with the following properties:
  \begin{itemize}
  \item $p = (i, n-1)$ for some $i$, and $p$ has no propagators inside it w.r.t the $<_i$ ordering \st{(that is $i+2, \ldots, n-2$ do not support any propagators in $W'$)}.
  \item Either the edge $i$ in $W'$ only supports $p$, or the edge $i$ in $W'$ supports exactly one other propagator $q = (j,i)$, with no other propagators inside $q$ in the $<_j$ ordering. 
  \end{itemize}
\end{lem}
Note that since the first condition tells us that $p$ has nothing inside it, if $q$ exists in the second condition then $j<_ji<_jn-1$.

@@

\begin{lem}\label{lem I}
Let $W$ be an admissible Wilson loop diagram with \hlfix{$k\geq 1$}{Here, as above, can we just say 'with more than one propagator?} propagators, and suppose that $W$ admits one of the configurations described in Lemma~\ref{lem good p}, with $p$ and $q$ (if $q$ exists) both of length 2. Let $V$ be $W$ with $p$ removed.  Then we can express $I_*^W$ in terms of $I_*^V$ as follows:

  \begin{align*}
    I_1^{W} & = I_1^{V} \cup \{n-3\} \\
    I_n^{W} & = I_1^{V} \cup \{n\} \\
    I_{n-1}^{W} & = I_n^{V} \cup \{n-1\} \\
    I_{n-2}^{W} & =
    \begin{cases}
      I_{n-2}^{V}\cup \{n-2\} & \text{if $n-2\not\in I_{n-2}^{V}$} \\
      I_{n-2}^{V}\cup \{n-1\} & \text{if $n-2\in I_{n-2}^{V}$, $n-1\not\in I_{n-2}^{V}$} \\
      (I_{n}^{V} - \{n-5\})\cup \{n-1,n-2\} & \text{if $n-1, n-2\in I_{n-2}^{V}$}
    \end{cases} \\
    I_{k}^{W} & =
    \begin{cases}
      I_k^{V}\cup \{n-3\} & \qquad \qquad \qquad \qquad \text{if $n-3 \not\in I_k^{V}$}\\
      I_k^{V}\cup\{n-2\} & \qquad \qquad \qquad \qquad \text{if $n-3\in I_k^{V}$}
    \end{cases} \\
    & \text{for $1<k<n-2$}
  \end{align*}
\end{lem}

@@

\begin{proof}
The two possible cases for $W$ are illustrated in Figure~\ref{fig special p}.

We first consider $I_1^{W}$, i.e. the set obtained by applying the Grassmann necklace algorithm to $W$ with starting vertex 1\note{I don't find this i.e. helpful at this point, is it an old thing that can go or do others find it useful?}. Note that $n-3 \not\in I_1^{V}$: for Case 2 this is clear from the diagram (since Algorithm~\ref{alg:put GN on WLD} would assign $q$ no later than vertex $n-4$), while for Case 1 it follows from Lemma \ref{lem no fourth vertex}. Therefore when we start at vertex 1 and apply the Grassmann necklace algorithm to $W$, $p$ is the only remaining unassigned propagator when we reach vertex $n-3$, and so we have $ I_1^{W}(p) = n-3$ and $I_1^W = I_1^V\cup \{n-3\}$.

Next consider $I_n^{W}$. From the figure we see that in both cases we have $I_n^{W}(p) = n$. At vertex 1 of the algorithm $I_n$, the unassigned propagators are exactly those that appear in $V$. Therefore the algorithm continues as in $I_1^{V}$ (recall Remark~\ref{rmk algorithm locally same} about locally identical propagator configurations), i.e. we have $I_n^{W} = I_1^{V} \cup \{n\}$. By a similar argument, we must have $I_{n-1}^{W} = I_n^{V} \cup \{n-1\}$.

Now consider $I_{n-2}^{W}$. If $n-2\not\in I_{n-2}^{V}$ (i.e. the vertex $n-2$ supports no propagators in $V$), then ${I_{n-2}^W(p) = n-2}$ and this assignment of $p$ does not affect the rest of the construction of $I_{n-2}^{V}$, so we obtain ${I_{n-2}^{W} = I_{n-2}^{V}\cup \{n-2\}}$ as above.

On the other hand, if $n-2\in I_{n-2}^{V}$ then we must be in Case 2 of Figure~\ref{fig special p} and $I_{n-2}^V(q) = I_{n-2}^W(q) = n-2$ (since $q$ is always the clockwise-most propagator supported on vertex $n-2$; see Figure~\ref{fig special p}). If $n-1 \not\in I_{n-2}^{V}$, then $I_{n-2}^W(p) = n-1$ and then the algorithm proceeds identically to $I_{n-2}^{V}$ for the remainder of its steps; thus $I_{n-2}^{W} = I_{n-2}^{V}\cup \{n-1\}$ in this case.

Finally, if $n-2,n-1 \in I_{n-2}^{V}$ then $I_{n-2}^W(q) = n-2$ and $I_{n-2}^W(p) = n-1$ as above, but this is different to what occured in $I_{n-2}^{V}$ so we cannot use the same argument as above. When the algorithm $I_{n-2}^W$ reaches vertex $n$, only the propagators $p$ and $q$ have contributed; thus we proceed as in the construction of $I_n^{V}$ but without propagator $q$. By Lemma~\ref{vertex cyclic int lem} we know that $I_n^V(q) = n-5$, and from the diagram we see that the only way this could occur is if all other propagators in $V$ had already been assigned when we reached vertex $n-5$; thus $q$ was the final propagator to be assigned in $I_n^{V}$. Therefore $I_{n-2}^{W} = (I_{n}^{V} \setminus \{n-5\}) \cup \{n-1, n-2\}$ in this case. This completes all cases for $I_{n-2}^{W}$.

@@

\begin{figure}
\[
\begin{tikzpicture}[rotate = 150,baseline=(current bounding box.east),label distance = -2mm]
\begin{scope}
	\drawWLDfragment[6]{3}{0.3}
	%\drawnumbers % use this to debug
	\begin{scope}
		\clipcenterarc(0,0)(\startpoint:\endpoint:\radius)
		\draw[smallpropagator] (\zero+2.4*\step:\radius*1.1) to [bend left = 55] (\zero + 4.6*\step:\radius*1.1); 
		\node at (\zero + 3.5*\step:\radius*0.75){\footnotesize $p$};
	\end{scope}
	\centerarc[red,line width = 2pt,line cap = round](0,0)(\zero + 2*\step:\zero+4.45*\step:\radius)
	\newbetternode[{[label distance=-3mm]above right}]{1}{n-4}
	\newbetternode[{[label distance=-3mm]above right}]{2}{n-3}
	\newbetternode[{[label distance=-3mm]above right}]{3}{n-2}
	\newbetternode[{[label distance=-3mm]above right}]{4}{n-1}
	\newnode[above]{5}{n}
	\newnode[above]{6}{1}
	\node at (180-60:\radius*0.1){\em Case 1};
\end{scope}
\end{tikzpicture}
\qquad 
\qquad 
\begin{tikzpicture}[rotate=150, baseline=(current bounding box.east)]
\begin{scope}
	\drawWLDfragment[7]{3}{0.3}
	%\drawnumbers % use this to debug
	\begin{scope}
		\clipcenterarc(0,0)(\startpoint:\endpoint:\radius)
		\draw[smallpropagator] (\zero+1.4*\step:\radius*1.1) to [bend left = 60] (\zero + 3.5*\step:\radius*1.1); 
		\draw[smallpropagator] (\zero+3.5*\step:\radius*1.1) to [bend left = 60] (\zero + 5.6*\step:\radius*1.1); 
		\node at (\zero + 2.4*\step:\radius*0.8){\footnotesize $q$};
		\node at (\zero + 4.5*\step:\radius*0.8){\footnotesize $p$};
	\end{scope}
	\centerarc[red,line width = 2pt,line cap = round](0,0)(\zero + 1.6*\step:\zero+5.5*\step:\radius)
	\newbetternode[{[label distance=-3mm]above right}]{1}{n-5}
	\newbetternode[{[label distance=-3mm]above right}]{2}{n-4}
	\newbetternode[{[label distance=-3mm]above right}]{3}{n-3}
	\newbetternode[{[label distance=-3mm]above right}]{4}{n-2}
	\newbetternode[{[label distance=-3mm]above right}]{5}{n-1}
	\newnode[above]{6}{n}
	\newnode[above]{7}{1}
	\node at (180-60:\radius*0.1){\em Case 2};
\end{scope}
\end{tikzpicture}
\]
  \caption{The two cases for $W$ and $p$.  No other propagators can end in the red sections.  Other segments may have additional propagators ending in them.}\label{fig special p}
\end{figure}

@@

Recall that $I_1$ determines the shape of the Le diagram: specifically, the elements of $I_1$ label the rows of the diagram, working from top right to bottom left. By the arguments in Lemma~\ref{lem I} we know that ${n,n-1,n-2, n-3 \not\in I_1^{V}}$ (which yields the leftmost four columns of the diagram for $V$) and that $I_1^{W} = I_1^{V}\cup \{n-3\}$. This implies that the right hand boundary of the shape of $V$ is the same as the right hand boundary of the shape of $W$ except that $W$ has one additional row of 3 boxes while $V$ has an additional column in the $n-3$ position; that is, an extra column fourth from the left. 
\end{proof}
\begin{figure}
  \[\includegraphics{Le_diagrams}\]
  \caption{Le diagrams for $V$ (left) and $W$ (right).}\label{fig Le}
\end{figure}

As illustrated in Figure~\ref{fig Le}, the pieces of the Le diagrams of $V$ and $W$ will be called $\mathcal{A}$ and $\mathcal{B}$ in what follows. \hlfix{Explicitly, $\mathcal{B}$ is the set of columns with labels $v < n-3$ and $\mathcal{A}$ is the set of columns labeled by $n$, $n-1$ and $n-2$ in $V$. In $W$, $\mathcal{A}$ consists of these columns without the last row.}{is this accurate?}\note{I think it is accurate} Over the course of the next few lemmas we will prove that the plusses in the $\mathcal{B}$ parts of each diagram are identical, and that the relationship between the plusses in the $\mathcal{A}$ regions can be described explicitly.

@@

\begin{lem}\label{lem n and n-1}
Let $V$ and $W$ be as in Lemma~\ref{lem I}.
Then $I_n^{W}$ and $I_{n-1}^{W}$ together yield the same plusses as $I_n^{V}$ did, along with two extra plusses which appear in the leftmost two boxes of the bottom row of the Le diagram of $W$.
\end{lem}

@@

Also by Lemma~\ref{lem I} we have $I_{n-1}^{W} = I_n^{V} \cup \{n-1\}$. Recall from the proof of Lemma~\ref{lem I} that $n-3,n-2,n-1,n \not\in I_1^V$; therefore $I_1^W\setminus I_{n-1}^W = (I_1^V \setminus I_n^V) \cup\{n-3\}$, and $n-3$ is maximal in this set. Similarly, 
\[I_{n-1}^W \setminus I_1^W = (I_n^V \setminus I_1^V) \cup \{n-1\} \subseteq \{n-1,n\},\]
where the final inclusion follows from the definition of Grassmann necklace. In particular, $n-1$ is minimal in this set, so Algorithm~\ref{alg:GN to Le} yields a plus in the $(n-3) \rightarrow (n-1)$ position (i.e. the second box in the bottom row of the Le diagram of $W$) along with any plusses yielded by $I_n^V$.
\end{proof}

@@

\begin{proof}
If $n-2\not\in I_{n-2}^{V}$ then $I_{n-1}^{V}=I_{n-2}^{V}$ by definition, and by Lemma~\ref{lem I} we have the equality ${I_{n-2}^{W} = I_{n-1}^{V} \cup \{n-2\}}$.  Note that $n-3\not\in I_{n-2}^{V}$ by Lemma~\ref{lem no fourth vertex}.  Therefore the paths controlling the plusses contributed by $I_{n-2}^{W}$ are exactly the paths for $I_{n-1}^{V}$ along with the $(n-3)\rightarrow (n-2)$ path.  This gives the statement of the lemma.
\end{proof}

@@

\section{Poles of Wilson Loop Integrals}\label{sec poles}

>>>>

\begin{lem}\label{lem sian} \sanote{should this be rephrased more similarly to the philosophy of Lemma 4.4, allowing non-supporting vertices to be added in or taken out?}
  Let $W$ be a weakly admissible WLD with at least 5 vertices and in which each vertex supports at least one propagator.  Then at least one of the following two things occurs.
  \begin{enumerate}
    \item $W$ has a propagator of length $\leq 6$ with a propagator of length 2 on one side of it and nothing else on that side.\label{item big and 2}
    \item There exists a pair of propagators of length $2$ with the property that the first propagator is $(i, i+2)$, the second is $(j, j+2)$, no other propagator ends between vertices $i+2$ and $j+1$, and $j\in\{i+2, i+3, i+4\}$.\label{item pair of 2s}
  \end{enumerate}
\end{lem}
\note{Should this lemma have pictures}

@@

\begin{rmk} \label{clockwise ordering rem}
When $p$ contributes $I_i(p) = a$, it must be the clockwise-most propagator supported on $a$ that has not yet contributed to $I_i$. i.e. any propagator supported on $a$ that appears later in the ordering given by $I_i$ must be inside $(p, <_{a})$.
\end{rmk}

@@

 \note{Remember to keep an eye out when proofreading: do we just need the vertices appearing in the GN element to be the same, or do we actually need the functions to match up} \sanote{need functions to match in 4.4}

@@

Let $W = (\cP,[n])$ be an admissible Wilson loop diagram\st{, and}{\color{violet}. For every }$p = (i,j) \in \cP$\st{.  Then}{\color{violet}, the sets} $J_p^{W}(i)$, $J_p^{W}(i+1)$, $J_p^{W}(j)$, and $J_p^{W}(j+1)$ are each non-empty cyclic intervals which partition $[n]$ and occur in the given cyclic order.
\end{lem}
\sanote{is there a way to express the cyclic intervals more easily than the cases in this proof?}
\begin{proof}
We will prove the result by induction on the number of propagators.  If $W$ has one propagator then the result is immediate.  Now suppose $W$ has more than one propagator.  Since non-supporting vertices have no effect on Algorithm~\ref{alg:put GN on WLD}, it suffices to prove the result for $W$  (possibly weakly admissible) with \st{$F(\emptyset) = \emptyset$}{\color{violet} no non-supporting vertices}.  Then by Lemma~\ref{lem sian}, $W$ has at least one of the four situations illustrated in Figure~\ref{fig 3 cases}.

@@

We first calculate $I^{W}_w$ for a starting vertex ${w \in [n]\backslash \{l, l+1, \ldots,j,j+1\}}$. \hlfix{Note that $p$ has no effect on other propagators for starting vertices in this range,}{By rmk \ref{rmk algorithm locally same}? If so, the entire proof depends on this fact. We should state it prominently and move on.} so if $r \neq p$, then $I_w^W(r) = I_w^V(r)$. Meanwhile, the value of $I^{W}_w(p)$ depends on which step in the algorithm the propagator $q$ \hlfix{is assigned to}{did the change from assign to contribute never happen?} a vertex {\color{violet} in the diagram $V$}, i.e. on the value of $I^{V}_w(q)$. Thus, if $w\in J_q^{V}(i)$ then 
    \[
    I_w^{W}(r) =  \begin{cases}
        \max\{i+1, m\} & \text{if } r=p \\
        I_{w}^{V}(r) & \text{if } r\neq p
      \end{cases} 
    \]
    while if $w\in J_q^{V}(i+1)$ or $w\in J_q^{V}(j)$ then
    \[
    I_w^{W}(r) =  \begin{cases}
        l & \text{if } r=p \\
        I_{w}^{V}(r) & \text{if } r\neq p
      \end{cases} 
      \]
We also need to understand $I^{W}_w$ for $w \in \{l,l+1,\ldots,j,j+1\}$. For the majority 
%$w \in [l, l+a-1]$} 
%I left this as a comment so we can add it in if necessary, but I don't think we need this level of precision in this sentence: we're just signposting what we're going to do in detail shortly.
of these vertices, we use the following observation: if $p$ is the first propagator to be assigned a value by $I_w^{W}$, then the remainder of $I_w^{W}$ proceeds identically to the assignments of $I^{V}_{w+1}$ (recall Remark~\ref{rmk algorithm locally same}).  Thus we have for any $0\leq b <a$
    \[
    I_{l+b}^{W}(r) = \begin{cases}
      l+b & \text{if } r=p\\
      I_{l+b+1}^{V}(r) & \text{if } r\neq p
    \end{cases}
    \]
Similarly, if $j$ is in the support of $p$, then we have
     \[
       I_j^{W}(r) = \begin{cases}
         j & \text{if $r=p$ and $j$ is in the support of $p$}\\
         I_{j+1}^{V}(r) & \text{if $r\neq p$ and $j$ is in the support of $p$}\\
       \end{cases}
       \]
If $j$ is not in the support of $p$, then we must be in Case 2 of Figure~\ref{fig 3 cases} with two vertices in the right hand region.  In this case, if we start the algorithm at $j$ we need to know whether there will be any unassigned propagators other than $p$ when we reach vertex $i$, so as to know what $p$ contributes.

@@

\begin{lem}\label{lem good p}
  Let $W$ be an admissible Wilson loop diagram with $k \geq 1$ propagators.  Then there is some dihedral transformation of $W$ such that the resulting diagram $W'$ has a propagator $p$ with the following properties:
  \begin{itemize}
  \item $p = (i, n-1)$ for some $i$, and $p$ has no propagators inside it w.r.t the $<_i$ ordering \st{(that is $i+2, \ldots, n-2$ do not support any propagators in $W'$)}.
  \item Either the edge $i$ in $W'$ only supports $p$, or the edge $i$ in $W'$ supports exactly one other propagator $q = (j,i)$, with no other propagators inside $q$ in the $<_j$ ordering. 
  \end{itemize}
\end{lem}
Note that since the first condition tells us that $p$ has nothing inside it, if $q$ exists in the second condition then $j<_ji<_jn-1$.

@@

\begin{lem}\label{lem I}
Let $W$ be an admissible Wilson loop diagram with $k\geq 1$ propagators, and suppose that $W$ admits one of the configurations described in Lemma~\ref{lem good p}, with $p$ and $q$ (if $q$ exists) both of length 2. Let $V$ be $W$ with $p$ removed.  Then we can express $I_*^W$ in terms of $I_*^V$ as follows:

  \begin{align*}
    I_1^{W} & = I_1^{V} \cup \{n-3\} \\
    I_n^{W} & = I_1^{V} \cup \{n\} \\
    I_{n-1}^{W} & = I_n^{V} \cup \{n-1\} \\
    I_{n-2}^{W} & =
    \begin{cases}
      I_{n-2}^{V}\cup \{n-2\} & \text{if $n-2\not\in I_{n-2}^{V}$ (Case 1)} \\
      I_{n-2}^{V}\cup \{n-1\} & \text{if $n-2\in I_{n-2}^{V}$, $n-1\not\in I_{n-2}^{V}$} \\
      (I_{n}^{V} - \{n-5\})\cup \{n-1,n-2\} & \text{if $n-1, n-2\in I_{n-2}^{V}$}
    \end{cases} \\
    I_{k}^{W} & =
    \begin{cases}
      I_k^{V}\cup \{n-3\} & \qquad \qquad \qquad \qquad \text{if $n-3 \not\in I_k^{V}$ (Case 1)}\\
      I_k^{V}\cup\{n-2\} & \qquad \qquad \qquad \qquad \text{if $n-3\in I_k^{V}$ (Case 2)}
    \end{cases} \\
    & \text{for $1<k<n-2$}
  \end{align*}
\end{lem}

@@

The two possible cases for $W$ are illustrated in Figure~\ref{fig special p}.

\begin{figure}
\[
\begin{tikzpicture}[rotate = 150,baseline=(current bounding box.east),label distance = -2mm]
\begin{scope}
	\drawWLDfragment[6]{3}{0.3}
	%\drawnumbers % use this to debug
	\begin{scope}
		\clipcenterarc(0,0)(\startpoint:\endpoint:\radius)
		\draw[smallpropagator] (\zero+2.4*\step:\radius*1.1) to [bend left = 55] (\zero + 4.6*\step:\radius*1.1); 
		\node at (\zero + 3.5*\step:\radius*0.75){\footnotesize $p$};
	\end{scope}
	\centerarc[red,line width = 2pt,line cap = round](0,0)(\zero + 2*\step:\zero+4.45*\step:\radius)
	\newbetternode[{[label distance=-3mm]above right}]{1}{n-4}
	\newbetternode[{[label distance=-3mm]above right}]{2}{n-3}
	\newbetternode[{[label distance=-3mm]above right}]{3}{n-2}
	\newbetternode[{[label distance=-3mm]above right}]{4}{n-1}
	\newnode[above]{5}{n}
	\newnode[above]{6}{1}
	\node at (180-60:\radius*0.1){\em Case 1};
\end{scope}
\end{tikzpicture}
\qquad 
\qquad 
\begin{tikzpicture}[rotate=150, baseline=(current bounding box.east)]
\begin{scope}
	\drawWLDfragment[7]{3}{0.3}
	%\drawnumbers % use this to debug
	\begin{scope}
		\clipcenterarc(0,0)(\startpoint:\endpoint:\radius)
		\draw[smallpropagator] (\zero+1.4*\step:\radius*1.1) to [bend left = 60] (\zero + 3.5*\step:\radius*1.1); 
		\draw[smallpropagator] (\zero+3.5*\step:\radius*1.1) to [bend left = 60] (\zero + 5.6*\step:\radius*1.1); 
		\node at (\zero + 2.4*\step:\radius*0.8){\footnotesize $q$};
		\node at (\zero + 4.5*\step:\radius*0.8){\footnotesize $p$};
	\end{scope}
	\centerarc[red,line width = 2pt,line cap = round](0,0)(\zero + 1.6*\step:\zero+5.5*\step:\radius)
	\newbetternode[{[label distance=-3mm]above right}]{1}{n-5}
	\newbetternode[{[label distance=-3mm]above right}]{2}{n-4}
	\newbetternode[{[label distance=-3mm]above right}]{3}{n-3}
	\newbetternode[{[label distance=-3mm]above right}]{4}{n-2}
	\newbetternode[{[label distance=-3mm]above right}]{5}{n-1}
	\newnode[above]{6}{n}
	\newnode[above]{7}{1}
	\node at (180-60:\radius*0.1){\em Case 2};
\end{scope}
\end{tikzpicture}
\] 
  \caption{The two cases for $W$ and $p$.  No other propagators can end in the red sections.  Other segments may have additional propagators ending in them.}\label{fig special p}

\end{figure} \sanote{moved figure before theorem 4.4 so that we can just refer to generically}
\begin{proof}

We first consider $I_1^{W}$, i.e. the set obtained by applying the Grassmann necklace algorithm to $W$ with starting vertex 1\note{I don't find this i.e. helpful at this point, is it an old thing that can go or do others find it useful?} \sanote{agreed, i vote to cut}. Note that $n-3 \not\in I_1^{V}$: \hlfix{for Case 2 this is clear from the diagram (since Algorithm {\ref{alg:put GN on WLD}} would force $q$ to contribute no later than vertex $n-4$),}{why? isn't obvious to me without several cases, and even then} while for Case 1 it follows directly from Lemma \ref{lem no fourth vertex}. Therefore when we start at vertex 1 and apply the Grassmann necklace algorithm to $W$, $p$ is the \st{only remaining unassigned propagator when we reach vertex $n-3$}{\color{violet}last propagator to contribute}, and so we have $ I_1^{W}(p) = n-3$ and $I_1^W = I_1^V\cup \{n-3\}$.

Next consider $I_n^{W}$. From the figure we see that in both cases we have $I_n^{W}(p) = n$. \hlfix{Therefore, the second through $k^{th}$ propagators contributing to $I_n^W$ are the same as the ordering in $I_n^V$. Since $n$ is non-supporting in $V$, $I_1^V = I_n^V$, we have $I_n^{W} = I_1^{V} \cup \{n\}$}{Alt. argument.  Can ignore.} At vertex 1 of the algorithm $I_n$, the unassigned propagators are exactly those that appear in $V$. Therefore the algorithm continues as in $I_1^{V}$ (recall Remark~\ref{rmk algorithm locally same} about locally identical propagator configurations), i.e. we have $I_n^{W} = I_1^{V} \cup \{n\}$. By a similar argument, we must have $I_{n-1}^{W} = I_n^{V} \cup \{n-1\}$.

Now consider $I_{n-2}^{W}$. If $n-2\not\in I_{n-2}^{V}$ \hlfix{by Corrollary {\ref{no coloops}}  $n-2$ is non-supporting in $V$. Thus we are in Case 1, with ${I_{n-2}^W(p) = n-2}$. By the arguments above ${I_{n-2}^{W} = I_{n-2}^{V}\cup \{n-2\}}$}{Alt. Argument. Can ignore} (i.e. the vertex $n-2$ supports no propagators in $V$), then ${I_{n-2}^W(p) = n-2}$ and this assignment of $p$ does not affect the rest of the construction of $I_{n-2}^{V}$, so we obtain ${I_{n-2}^{W} = I_{n-2}^{V}\cup \{n-2\}}$ as above.

On the other hand, if $n-2\in I_{n-2}^{V}$ then we must be in Case 2 of Figure~\ref{fig special p} and $I_{n-2}^V(q) = I_{n-2}^W(q) = n-2$ \st{(since $q$ is always the clockwise-most propagator supported on vertex $n-2$; see Figure {\ref{fig special p}})}. If $n-1 \not\in I_{n-2}^{V}$, then $I_{n-2}^W(p) = n-1$ and then the algorithm proceeds identically to $I_{n-2}^{V}$ for the remainder of its steps; thus $I_{n-2}^{W} = I_{n-2}^{V}\cup \{n-1\}$ in this case.

Finally, if $n-2,n-1 \in I_{n-2}^{V}$ then $I_{n-2}^W(q) = n-2$ and $I_{n-2}^W(p) = n-1$ as above, but \st{this is different to what occured in $I_{n-2}^{V}$}{\color{violet}but some other propagator must contribute $n-1$ to $I_{n-2}^{V}$} so we cannot use the same argument as above. When the algorithm $I_{n-2}^W$ reaches vertex $n$, only the propagators $p$ and $q$ have contributed; thus we proceed as in the construction of $I_n^{V}$ but without propagator $q$ by Remark \ref{rmk algorithm locally same}. By Lemma~\ref{vertex cyclic int lem} we know that $I_n^V(q) = n-5$ \sanote{it would be nice if this were easier to read from lemma without digging through proof}, and from \st{the diagram }{\color{violet} Remark \ref{clockwise ordering rem} } we see that the only way this could occur is if $q$ was the last to contribute to $I_{n-2}^V$. %all other propagators in $V$ had already been assigned when we reached vertex $n-5$; thus $q$ was the final propagator contributing to $I_n^{V}$. 
Therefore $I_{n-2}^{W} = (I_{n}^{V} \setminus \{n-5\}) \cup \{n-1, n-2\}$ in this case. This completes all cases for $I_{n-2}^{W}$.

@@

@@

Recall that $I_1$ determines the shape of the Le diagram: specifically, the elements of $I_1$ label the rows of the diagram, working from top right to bottom left. By the arguments in Lemma {\ref{lem I}} we know that \st{${n,n-1,n-2, n-3 \not\in I_1^{V}}$}\sanote{Only see $n-3$ in Lemma 4.4?} {\color{violet} $ n-3 \not\in I_1^{V}$. By Lemma \ref{lem no fourth vertex}, $n, n-2 \not \in I_1^V$. Since $n-1$ is non-supporting in $V$, by Corrollary {\ref{no coloops}}, $n \not\in I_1^{V}$.} These are the leftmost four columns of the diagram for $V$.  From Lemma \ref{lem I} we know that that $I_1^{W} = I_1^{V}\cup \{n-3\}$. Therefore, the right hand boundary of the shape of $V$ is the same as the right hand boundary of the shape of $W$ except that $W$ has one additional row of 3 boxes while $V$ has an additional column in the $n-3$ position; that is, an extra column fourth from the left. 
\end{proof}
\begin{figure}
  \[\includegraphics{Le_diagrams}\]
  \caption{Le diagrams for $V$ (left) and $W$ (right).}\label{fig Le}
\end{figure}

As illustrated in Figure~\ref{fig Le}, the pieces of the Le diagrams of $V$ and $W$ will be called $\mathcal{A}$ and $\mathcal{B}$ in what follows. Explicitly, $\mathcal{B}$ is the set of columns with labels $v < n-3$ and $\mathcal{A}$ is the set of columns labeled by $n$, $n-1$ and $n-2$ in $V$. In $W$, $\mathcal{A}$ consists of these columns without the last row. Over the course of the next few lemmas we will prove that the plusses in the $\mathcal{B}$ parts of each diagram are identical, and that the relationship between the plusses in the two $\mathcal{A}$ regions can be described explicitly.

@@

\begin{lem}\label{lem n and n-1}
Let $V$ and $W$ be as in Lemma~\ref{lem I}.
Then \hlfix{$I_n^{W}$}{Does $I_n^W$ actually yeild any of the $+$s in $I_n^V$?} and $I_{n-1}^{W}$ together yield the same plusses as $I_n^{V}$ did, along with two extra plusses which appear in the leftmost two boxes of the bottom row of the Le diagram of $W$.
\end{lem}

@@

Also by Lemma~\ref{lem I} we have $I_{n-1}^{W} = I_n^{V} \cup \{n-1\}$. Recall from the proof of Lemma \st{{\ref{lem I}}} {\color{violet} {\ref{lem shape}} }\sanote{change back if actually in 4.4} that $n-3,n-2,n-1,n \not\in I_1^V$; therefore $I_1^W\setminus I_{n-1}^W = (I_1^V \setminus I_n^V) \cup\{n-3\}$, and $n-3$ is maximal in this set. Similarly, 
\[I_{n-1}^W \setminus I_1^W = (I_n^V \setminus I_1^V) \cup \{n-1\} \subseteq \{n-1,n\},\]
where the final inclusion follows from the definition of Grassmann necklace\sanote{why only $\{n-1,n\}$? I'd believe an inclusion the other way}. In particular, $n-1$ is minimal in this set, so Algorithm~\ref{alg:GN to Le} yields a plus in the $(n-3) \rightarrow (n-1)$ position (i.e. the second box in the bottom row of the Le diagram of $W$) \hlfix{along with any plusses yielded by $I_n^V$.}{display seems to imply that there is exactly one such other $+$. Is this correct?}
\end{proof}

@@

\begin{proof}
If $n-2\not\in I_{n-2}^{V}$ then $I_{n-1}^{V}=I_{n-2}^{V}$ by definition, and by Lemma~\ref{lem I} we have the equality ${I_{n-2}^{W} = I_{n-1}^{V} \cup \{n-2\}}$.  Note that $n-3\not\in I_{n-2}^{V}$ by Lemma~\ref{lem no fourth vertex}.  Therefore the \st{paths controlling the} plusses contributed by $I_{n-2}^{W}$ are exactly the \st{paths for}{\color{violet} plusses from}\sanote{isn't this from Alg.\ref{alg:GN to Le} which says nothing about paths?}  $I_{n-1}^{V}$ along with the $(n-3)\rightarrow (n-2)$ path.  This gives the statement of the lemma.
\end{proof}

@@

\section{Poles of Wilson Loop Integrals}\label{sec poles} \sanote{start here}
